Reproducible Validation and Replication Studies in Nanoscale Physics

### 2020-07-25 tex/results.tex
add some more edits

We first aim to replicate the computational result presented in Figure S4 of their supplementary 
material that correspond to the black curve on their plot. In this 
figure they show simulation results for the resonance spectral position of the lower frequency 
mode when having parallel polarization ($E^{\parallel}_{100}$), with an incidence angle of 22$^\circ$.
We attempted to replicate this result since the gap between the pillars 
is 5000 nm (10 times more than other results), diminishing the effects of coupling, which makes it 
a good candidate to replicate using \pygbe.

@@

\textit{methods}
(I DID NOT MENTION ANYTHING RELATED TO WHAT THEY DO IN THE EXPERIMENTS, SHOULD WE INCLUDE THIS?)

In Ellis et al. simulations they solve full Maxwell equations via the RF package of the finite
element method software COMSOL. To represent the array of pillars and their interactions, they use
periodic boundary conditions of one pillar over a portion of substrate, and use periodic boundary conditions on it.
They present the reflectance as a function of the wave number. 
As we mentioned before, we use the boundary element method in 
the quasistatic approximation, which is suitable in these case since Ellis pillar's size is small 
compared to the wavelength involved in the simulations (800-1000 cm$^-1$ which is 10000-12500 nm). We measure 
extinction cross section, which will express as peaks instead of depressions (as seen in Ellis reflection plots)
since you see maximum extinction when there is minimum reflection. The intensity of the peaks is not comparable, but we are 
looking to match the wave number (variable of interest) at which these events happen.

>>>>

We first aim to replicate the computational result presented in Figure S4 of their supplementary 
material that correspond to the black curve on their plot. In this 
figure they show simulation results for the resonance spectral position of the lower frequency 
mode when having parallel polarization ($E^{\parallel}_{100}$), with an incidence angle of 22$^\circ$.
We attempted to replicate this result since the gap between the pillars 
is 5000 nm (10 times more than other results), diminishing the effects of coupling, which makes it 
a good candidate to replicate using \pygbe. Secondly, we will perform a second attempt of replication  
for the results presented in Figure 2a, in which they present reflectance measurements across wave number
for pillars with AR=4 for an angle of incidence of 22 degrees and incoming polarization parallel to the 
length of the pillars.

@@

\textit{methods}

In Ellis et al. they run experiments using reflectance spectroscopy and they compute the solution of
Maxwell equations via the RF package of the finite element method software COMSOL. In their simulations 
they use periodic boundary conditions of one pillar over a portion of substrate, to represent the array of 
pillars and their interactions. 
We use the boundary element method in the quasistatic approximation, which is suitable in these case 
since the pillar's size is small compared to the wavelength involved in the simulations (800-1000 cm$^-1$ which is 10000-12500 nm). 
We measure extinction cross section, which will express as peaks instead of depressions (as seen in Ellis reflection plots). 
The intensity of the peaks is not comparable, but we are looking to match the wave number (variable of interest) at which these events happen.
